---
title: "Pokédex Explorer — Stat Map Module"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: journal
runtime: shiny
---

```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(shiny)
```

<style>
/* Pokémon-themed module titles */
.dex-title {
  font-family: serif;
  font-size: 118%;
  font-weight: bold;
  color: #3b2f23;
  margin-bottom: 4px;
}

/* Warm-toned captions */
.caption-warm {
  font-style: italic;
  color: #6a604d;
  font-size: 90%;
}

/* Dashed field-guide separator */
hr.field-sep {
  border-top: 1px dashed #b8ad99;
  margin-top: 8px;
  margin-bottom: 8px;
  opacity: 0.8;
}

/* Notes card look */
.notes-card {
  background-color: #faf7f0;
  border: 1px solid #d5ccb8;
  padding: 10px 12px;
  border-radius: 6px;
}

/* Trainer control panel styling (tight, clean) */
.trainer-panel {
  background-color: #fdfaf4;
  border: 1px solid #e0d4bd;
  border-radius: 6px;
  padding: 8px 10px;
}

/* Stat map panel styling with faint Pokéball ring (tight, clean) */
.map-panel {
  background: radial-gradient(circle at 30% 30%, rgba(229, 59, 59, 0.08) 0, rgba(229, 59, 59, 0.0) 55%),
              #fefdf8;
  border: 1px solid #e0d4bd;
  border-radius: 6px;
  padding: 8px 10px;
}

/* Pokédex-style labels for controls */
.control-label {
  font-weight: 600;
  font-size: 88%;
  letter-spacing: 0.04em;
  text-transform: uppercase;
  color: #3b2f23;
  margin-top: 4px;
  margin-bottom: 2px;
}

/* Reduce default margin on h3 section headers */
.section.level3 > h3 {
  margin-top: 4px;
  margin-bottom: 4px;
}
</style>

Explorer
=====================================

**Stat Explorer Module:** Visualizing how Pokémon stats relate to each other.  
<span class="caption-warm">A Pokédex-style analytical view of stat relationships.</span>

<hr class="field-sep">

Row {data-height=120}
-------------------------------------

### <span class="dex-title">Module 01 — Trainer Controls</span> {data-width=30}

<div class="trainer-panel">

<span class="caption-warm">Use these settings to customize your stat exploration as a trainer.</span>

```{r}
# Controls for map page — real data will be linked later

tagList(
  div(class = "control-label", "Primary Type Filter"),
  selectInput(
    "filter_type",
    NULL,
    choices = c("All"),
    selected = "All"
  ),
  div(class = "control-label", "Generation Filter"),
  selectInput(
    "filter_gen",
    NULL,
    choices = c("All"),
    selected = "All"
  ),
  div(class = "control-label", "X-Axis Stat"),
  selectInput(
    "x_stat",
    NULL,
    choices = c(
      "HP" = "hp",
      "Attack" = "attack",
      "Defense" = "defense",
      "Special Attack" = "special_attack",
      "Special Defense" = "special_defense",
      "Speed" = "speed"
    ),
    selected = "attack"
  ),
  div(class = "control-label", "Y-Axis Stat"),
  selectInput(
    "y_stat",
    NULL,
    choices = c(
      "HP" = "hp",
      "Attack" = "attack",
      "Defense" = "defense",
      "Special Attack" = "special_attack",
      "Special Defense" = "special_defense",
      "Speed" = "speed"
    ),
    selected = "defense"
  )
)
```


</div>

### <span class="dex-title">Module 02 — Stat Mapping Interface</span> {data-width=70}

<div class="map-panel">

<span class="caption-warm">Adjust filters and stat axes to visualize how different Pokémon are positioned in stat space.</span>

```{r}
# Placeholder plot — safe and error-free
renderPlot({
  ggplot2::ggplot(data.frame(x = 0, y = 0), ggplot2::aes(x, y)) +
    ggplot2::geom_point(alpha = 0) +
    ggplot2::labs(title = "Pokémon Stat Map") +
    ggplot2::theme_void()
})
```

</div>

Row
-------------------------------------

<hr class="field-sep">

### <span class="dex-title">Pokédex Field Notes</span> 🌿

<div class="notes-card">

**Design Notes (Melanie):**

- This is the layout for the Stat Map page of our Pokédex dashboard.  
- “Trainer Controls” and “Stat Mapping Interface” use Pokédex-style wording to match the theme.  
- The trainer panel groups all interactive controls in one place for a clean, guided experience.  
- The stat map panel uses a faint Pokéball ring effect and warm tones to keep the aesthetic subtle but thematic.  
- When the user changes the selected stats or filters, the coded version of this page will update the visualization in the map panel.  
- Kyle and Tayin will replace the placeholder plot with the real stat visualizations.  
- The `journal` theme plus custom styling blend a naturalist field-guide feel with a modern Pokédex interface.

</div>


Explorer
=====================================

**Stat Explorer Module:** Visualizing how Pokémon stats relate to each other.  
<span class="caption-warm">A Pokédex-style analytical view of stat relationships.</span>

<hr class="field-sep">

Row {data-height=120}
-------------------------------------

### <span class="dex-title">Module 01 — Trainer Controls</span> {data-width=30}

<div class="trainer-panel">

<span class="caption-warm">Use these settings to customize your stat exploration as a trainer.</span>

```{r}
# Controls for map page — real data will be linked later

tagList(
  div(class = "control-label", "Primary Type Filter"),
  selectInput(
    "filter_type",
    NULL,
    choices = c("All"),
    selected = "All"
  ),
  div(class = "control-label", "Generation Filter"),
  selectInput(
    "filter_gen",
    NULL,
    choices = c("All"),
    selected = "All"
  ),
  div(class = "control-label", "X-Axis Stat"),
  selectInput(
    "x_stat",
    NULL,
    choices = c(
      "HP" = "hp",
      "Attack" = "attack",
      "Defense" = "defense",
      "Special Attack" = "special_attack",
      "Special Defense" = "special_defense",
      "Speed" = "speed"
    ),
    selected = "attack"
  ),
  div(class = "control-label", "Y-Axis Stat"),
  selectInput(
    "y_stat",
    NULL,
    choices = c(
      "HP" = "hp",
      "Attack" = "attack",
      "Defense" = "defense",
      "Special Attack" = "special_attack",
      "Special Defense" = "special_defense",
      "Speed" = "speed"
    ),
    selected = "defense"
  )
)
```