---
title: "Pokédex Explorer"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: journal
runtime: shiny
css: styles.css
---

PokéStats 
=====================================

```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(shiny)
library(leaflet)
library(DT)
library(sf)
library(magick)
library(stringr)
library(htmltools)
```

```{r}
# Load Colorado ecotone data if available
if (file.exists("poke_data.RData")) {
  load("poke_data.RData")
  co_counties_map <- co_counties_ecotones %>% st_transform(4326)

  poke_by_county <- co_counties_map %>%
    st_drop_geometry() %>%
    select(NAME, ecotone) %>%
    inner_join(pokemon_clean_df, by = "ecotone", relationship = "many-to-many")
}
```

```{r}
# Load and transform pokemon_df

pokemon_df <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-04-01/pokemon_df.csv')

pokemon_evolution <- readxl::read_excel("pokemon_evolution.xlsx")

# Capitalize pokemon names 
pokemon_df$pokemon <- str_to_title(pokemon_df$pokemon)

# Filter pokemon_df to pokemon_evolution list and combine all evolution-related names into one character vector
evo_names <- pokemon_evolution %>%
  select(unevolved, evolution_one, evolution_two) %>%
  unlist(use.names = FALSE) %>%
  unique()

# Filter pokemon_df so pokemon matches any of those names
pokemon_df <- pokemon_df %>%
  filter(pokemon %in% evo_names) 

# Add reference columns to state what the base pokemon and evolution stage are 
evo_long <- pokemon_evolution %>%
  mutate(Base_pokemon = unevolved) %>% 
  pivot_longer(
    cols = c(unevolved, evolution_one, evolution_two),
    names_to = "Stage",
    values_to = "Pokemon"
  ) %>% 
  mutate(
    Evolution_stage = case_when(
      Stage == "unevolved"     ~ 0L,
      Stage == "evolution_one" ~ 1L,
      Stage == "evolution_two" ~ 2L
    )
  ) %>%
  drop_na() %>% 
  select(Pokemon, Base_pokemon, Evolution_stage) 

# Merge the evolution reference to pokemon_df
pokemon_df <- pokemon_df %>%
  left_join(evo_long %>% select(Pokemon, Base_pokemon, Evolution_stage),
            by = c("pokemon" = "Pokemon"))

# Re-order columns in pokemon_df and remove duplicated rows
pokemon_df <- pokemon_df %>%
  select(pokemon, Evolution_stage, Base_pokemon, everything()) %>% 
  distinct(pokemon, .keep_all = TRUE)

# Choices for the stat dropdown
stat_choices <- c(
  "HP"               = "hp",
  "Attack"           = "attack",
  "Defense"          = "defense",
  "Special Attack"   = "special_attack",
  "Special Defense"  = "special_defense",
  "Speed"            = "speed"
)
```

<div class="pokedex-panel-title">Evolution Module</div>

<div class="pokedex-card">
Explore a Pokémon’s stats, sprite, and full evolution line using the controls below.
</div>

Column {data-width=30}
-------------------------------------

### Trainer Controls {data-width=30, data-height=400}

```{r}
# Pokémon picker
tagList(
  div(class = "control-label", "Pokémon"),
  selectInput(
    "filter_pokemon",
    NULL,
    choices = c(sort(unique(pokemon_df$pokemon))),
    selected = "Eevee"
  )
)


# Wrap the stat radio buttons in a scrollable container
div(
  style = "
    max-height: 200px;
    overflow-y: auto;
    padding-right: 5px;
    margin-top: 5px;
  ",
  radioButtons(
    "power_stat",
    label = "Choose a stat to visualize:",
    choices = stat_choices,
    selected = "hp"
  )
)
```

### Evolution Stat Comparison {data-width=30}

```{r}
renderPlot({
selected <- input$filter_pokemon
stat_col <- input$power_stat
req(selected, stat_col)

# Find base family for selected pokemon 
base_name <- pokemon_df %>% 
  filter(pokemon == selected) %>% 
  pull(Base_pokemon)

# Get all pokemon in the same family + order by stage

evo_group <- pokemon_df %>% 
  filter(Base_pokemon == base_name) %>% 
  arrange(Evolution_stage)

# Ordered vector of Pokémon names for axis ordering
  evo_vec <- evo_group$pokemon

# Friendly label for the axis/title

stat_labels <- c(
hp              = "HP",
attack          = "Attack",
defense         = "Defense",
special_attack  = "Special Attack",
special_defense = "Special Defense",
speed           = "Speed")

y_lab <- stat_labels[[stat_col]]
  ggplot(
    evo_group,
    aes(x = .data[[stat_col]],
      y = factor(pokemon, levels = evo_group$pokemon),
      fill = type_1)
        ) +
    geom_col() +
    scale_x_continuous(expand = c(0,0)) + 
    theme_minimal() +
    theme(
      legend.position = "none",
      panel.grid = element_blank(),
      axis.line = element_line(color = "black", linewidth = 0.2),
      plot.title      = element_text(color = "black"),
      axis.title.x    = element_text(color = "black"),
      axis.title.y    = element_text(color = "black"),
      axis.text.x    = element_text(color = "black",
                                     angle = 30, 
                                     hjust = 1),
      axis.text.y     = element_text(color = "black"),
          ) +
    labs(
      title = paste(selected, "Evolution", y_lab, "Stats"),
      x = y_lab,
      y = "Pokémon"
        ) +
    coord_flip() 
})
```

Column {data-width=70}
-------------------------------------

### Pokémon Sprite Viewer {data-width=70, data-height=750}

```{r}
renderUI({
  selected <- input$filter_pokemon
  req(selected)

  poke <- pokemon_df %>%
    dplyr::filter(pokemon == selected) %>%
    dplyr::slice(1)

  url <- poke$url_image[1]

  if (is.na(url) || url == "") {
    return("No image available.")
  }

  # OUTER CENTERING WRAPPER  ✅ add class = "sprite-panel"
  div(
    class = "sprite-panel",
    style = "width:100%; display:flex; justify-content:center;
               overflow-y: auto;
    ",

    # ACTUAL CARD
    div(
      class = "pokemon-card",

      # CARD INNER LAYOUT
      div(
        class = "pokemon-card-inner",

        # LEFT: IMAGE
        tags$img(
          src = url,
          alt = selected,
          class = "pokemon-card-img"
        ),

        # RIGHT: INFO PANEL
        div(
          class = "pokemon-card-info",

          tags$h4(selected, class = "pokemon-card-name"),

          tags$ul(
            class = "pokemon-card-list",

            tags$li(paste("Height (m):", poke$height)),
            tags$li(paste("Weight (kg):", poke$weight)),
            tags$li(paste("Primary type:", poke$type_1)),
            tags$li(paste("Secondary type:", poke$type_2)),
            tags$hr(),

            tags$li(paste("Base experience:", poke$base_experience)),
            tags$li(paste("HP:", poke$hp)),
            tags$li(paste("Attack:", poke$attack)),
            tags$li(paste("Defense:", poke$defense)),
            tags$li(paste("Special Attack:", poke$special_attack)),
            tags$li(paste("Special Defense:", poke$special_defense)),
            tags$li(paste("Speed:", poke$speed)),
            tags$hr(),

            tags$li(paste("Base Pokémon:", poke$Base_pokemon)),
            tags$li(paste("Evolution stage:", poke$Evolution_stage)),
            tags$li(paste("Egg group:", poke$egg_group_1)),
            tags$li(paste("Pokémon Generation:", poke$generation_id))
          )
        )
      )
    )
  )
})
```

### Evolution Line {data-width=70}

```{r}
renderUI({
  selected <- input$filter_pokemon
  req(selected)

  # Find base family for the selected pokemon 
  base_name <- pokemon_df %>% 
    filter(pokemon == selected) %>% 
    pull(Base_pokemon)

  # Get all Pokémon in the same evolutionary family
  evo_df <- pokemon_df %>%
    filter(Base_pokemon == base_name) %>%
    arrange(Evolution_stage)   # ensures proper order

  if (nrow(evo_df) == 0) {
    return(tags$p("No evolution images available.", style = "color:#444;"))
  }

  div(
    class = "evolution-line-container",
    style = "
      height: 300px;
      overflow-y: auto;
      overflow-x: auto;
      padding: 5px;
      display: flex;
      gap: 10px;
      align-items: flex-start;
    ",
    lapply(seq_len(nrow(evo_df)), function(i) {
      tags$div(
        style = "
          display: inline-block;
          vertical-align: top;
          width: 150px;
          margin: 15px;
          text-align: center;
        ",
        # Pokémon image
        tags$img(
          src = evo_df$url_image[i],
          style = "
            max-height: 150px;
            width: 150px;
            object-fit: contain;
            display: block;
            margin: 0 auto;
          "
        ),
        # Pokémon name
        tags$p(
          evo_df$pokemon[i],
          style = "
            margin-top: 8px;
            font-size: 14px;
            font-weight: 600;
            color: #333;
          "
        )
      )
    })
  )
})
```


PokéMap 
=====================================

Column {data-width=65}
-------------------------------------

### Colorado PokéMap {data-width=65}

<div class="pokedex-card">
View where each Pokémon appears across Colorado’s ecotones. Select a Pokémon on the right to highlight its counties and view its ecotone, type, and generation.
</div>

```{r}
if (!exists("co_counties_map")) {
  renderLeaflet({ leaflet() })
} else {
  renderLeaflet({
    poke <- input$chosen_pokemon

    highlight <- poke_by_county %>%
      filter(pokemon == poke) %>%
      pull(NAME)

    fill <- ifelse(co_counties_map$NAME %in% highlight, "orange", "lightblue")

    leaflet(co_counties_map) %>%
      addTiles() %>%
      addPolygons(
        label = ~NAME,
        fillColor = fill,
        fillOpacity = 0.6,
        color = "white",
        weight = ifelse(co_counties_map$NAME %in% highlight, 4, 1)
      )
  })
}
```

Column {data-width=35}
-------------------------------------

### Pokémon Details {data-width=35}

```{r}
if (exists("poke_by_county")) {
  selectInput(
    "chosen_pokemon",
    "Select a Pokémon:",
    choices = sort(unique(poke_by_county$pokemon)),
    selected = "Eevee"
  )
}
```

```{r}
renderUI({
  req(input$chosen_pokemon)

  if (!exists("poke_by_county"))
    return("Colorado dataset unavailable.")

  row <- poke_by_county %>% filter(pokemon == input$chosen_pokemon) %>% slice(1)

  tags$div(
    tags$img(src = row$url_image[1], style = "max-width:500px; max-height:500px"),
    tags$p(paste("Ecotone:", row$ecotone), style = "font-size:25px"),
    tags$p(paste("Type:", row$type_1), style = "font-size:25px"),
    tags$p(paste("Generation:", row$generation_id), style = "font-size:25px")
  )
})
```


About 
=====================================

<div class="pokedex-about">
### Welcome Trainers! 

This Pokédex is designed to give you all the information you need to look for, catch and train your Pokémon for the Colorado Tournament of Champions. 

This tournament features challenges and obstacles that will take you through every ecosystem of Colorado and will require a team of Pokémon with diverse strengths and skills. Each Trainer may assemble up to 9 Pokémon to compete; we suggest a representative from each Colorado ecotone (Urban, Forest, Mountain, Agriculture, Water, Grassland, Riparian, Sand Dunes, and Steppe). Together, you and your Pokémon will compete in a melee-style Battle Royale against other teams and the elements in an arena designed to mimic the harshest challenges Colorado has to offer. 


As you set out to build your team, use our interactive map to track down Pokémon in each Colorado ecotone. To do so, select a Pokémon from the dropdown menu on the right side of the Pokémap portal. An image of your selection will be displayed along with its Ecotone, Type, and Generation. On the left, the map of Colorado will display the counties in which your select Pokémon may be found. 

Before trekking into the wilds (or urban areas) of Colorado to catch your Pokémon, read up on its stats and potential in the PokéStats portal. Here, again, you may select your Pokémon from the dropdown menu. An image of the selected Pokémon will be displayed along with detailed metrics on its natural history including size, powers, and evolution stage. Below the main image panel, images of all the variations in its evolutionary line will appear so you’ll know what’s in store should your Pokémon evolve. A final feature allows you to compare the power stats (HP, Defense, Attack, Special Defense, Special Attack and Speed) of the selected Pokémon to those in its evolution line. To do so, simply select the stat of interest from the left-hand panel of the portal, and see it visualized in the graphic beneath. 


We wish you luck, and we will see you on the battlefield.


Gotta catch ‘em all!

Sincerely,

PokéTeam 535

### **Data Source:**

TidyTudesday: Pokemon images, stats, life history

Pokemon Evolution: evolution stage

Kyles Ruszkowski: (ecotones of Colorado + the Pokemon that live there). 
</div>